\documentclass[11pt,a4paper]{article}

\begin{document}
\section*{Abstract}
In this work we perform a quantum chromodynamics (QCD) analysis on hadronic tau
decays. QCD is describing the strong force, which dictates the interactions of
quarks. Quarks are elementary particles. E.g. a proton is build of three quarks.
The strength of the interactions is given by the strong coupling constant, which
in contrary to its name is dependent on energy. In this thesis we will measure
the strong coupling from hadronic tau decays. The tau is the only known lepton
which is heavy enough to decay into hadrons. Nevertheless it lets us probe the
strong coupling for low energies. As the strong coupling decreases for higher
energies, so do the errors. The framework of extracting the strong coupling is
referred to as qcd sum rules. Within the sum rules we have to choose between
fixed-order perturbation theory (FOPT) or contour-improved perturbation theory
(CIPT). Both methods are equally valid, but lead to different values. To test
the validity of FOPT we make use of the Borel Summation (BS). The BS can be used
to give the best possible sum of divergent asymptotic series as the one we are
dealing with in by extracting the strong coupling. For low energies the coupling
is large and for high energies the coupling is small. This leads to confinement.
Quarks always appear as composite particles, the so-called Hadrons. Until today
we have never measured an isolated quark. This is problematic as QCD is a theory
describing quarks, but experiments are measuring hadrons. Consequently
quark-hadron duality has been introduced, which states that we can describe
physical quantities either in the quark-gluon picture or the hadronic picture,
and that both description are equally valid. Unfortunately the assumption of
duality is often violated. In theory we can suppress these duality violations
(DV) by applying so called pinched weights. The higher the pinching the more
suppressed are DV. We will perform fits for different weights to state, that
even for low pinching, DV are sufficiently suppressed to extract the strong
coupling.
\end{document}
