\documentclass[../../index.tex]{subfiles}

\begin{document}
\pdfbookmark[0]{Abstract}{abstract} % Sets a PDF bookmark for the abstract
\chapter*{Abstract}
In this work, we perform a \define{qcd}{quantum chromodynamics} analysis on
hadronic \(\tau\) decays. We make use of the \textsc{aleph} data to fit
the strong coupling and higher order \define{ope}{operator product expansion}
contributions. Our approach is based on the \define{qcdsr}{\textsc{qcd} sum
  rules}, especially the framework of \define{fopt}{fixed\-/order perturbation
  theory}, which we apply for the \define{v+a}{vector + axial\-/vector} channel
of the inclusive Cabibbo\-/allowed hadronic \(\tau\) decay data. We perform
fits using a new set of analytic weight functions to shed light on the
discussion of the importance of \define{dv}{duality violation}. Since the
inclusion of a model to parametrise contributions of \textsc{dv} by Boito et al.
\cite{Boito2011a} there has been an ongoing discussion, especially with the group
around Pich \cite{Pich2016}, which disfavours the usage of the \textsc{dv}
model. Within this work, we want to give a third opinion arguing that
\textsc{dv} are not present in double pinched weights. Even for single pinched
weights, we find that \textsc{dv} are sufficiently suppressed for high precision
measurements of the strong coupling. Another unsolved topic is the discussion of
\textsc{fopt} vs \define{cipt}{contour\-/improved perturbation theory}. Beneke
et al. \cite{Beneke2008} have found that \textsc{cipt} cannot reproduce the
\define{bs}{Borel summation}, while the creators of \textsc{cipt}
\cite{Pivovarov1991, LeDiberder1992a} are in favour of the framework. To
investigate the validity of \textsc{fopt} we apply the \textsc{bs}. The
parameters we obtain from both frameworks are in high agreement. Performing fits
in the framework of \textsc{cipt} lead to different results. Consequently, in
the discussion of \textsc{fopt} vs \textsc{cipt} we argue for \textsc{fopt}
being the favoured framework. For our final result of the strong coupling we
perform fits for ten different weights. For each weight, we further fit 20
different moments by varying the energy limit \(s_0\). We select the best fit of
each weight in a final comparison. The fits are in high agreement and the
average of the parameters we obtain yields a value of \(\alpha_s(m_\tau^2) =
0.3261(51) \) for the strong coupling, \(\rho^{(6)} = -0.68(20)\) for the
dimension six \textsc{ope} contribution and \(\rho^{(8)} = -0.80(38) \) for the
dimension eight \textsc{ope} contribution.

\end{document}